Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-02-24 paper/paper.tex
updated box plots to have two periods and paper and jobs for faster make Tested everything on node23.

\begin{figure}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
  \caption{Two box plots of triangle shapes.  The two smaller show
    sizes at the lower stability threshhold, one just below, one just
    above.  The larger triangle is the largest simulated. The vertical
    axis shows stacked and changing over time the total number of
    proteins that are of four different compound stages and in the
    different sections of the cell.}
  \label{box-triangle}
\end{figure}

@@

\section{Our 'V' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-500-500-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1500-1500-9900-1500}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1600-1600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1800-1800-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-2000-2000-9900-1500}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
  %\includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
  \caption{Two box plots of triangle shapes.  The two smaller show
    sizes at the lower stability threshhold, one just below, one just
    above.  The larger triangle is the largest simulated. The vertical
    axis shows stacked and changing over time the total number of
    proteins that are of four different compound stages and in the
    different sections of the cell.}
  \label{box-triangle}
\end{figure}

@@

\section{Our 'V' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
\end{figure}
